Microclimatic spatial variation buffers local warming in alpine vegetation

### 2022-02-16 doc/manuscript.Rmd
glm species models 🔮

```{r}
library(vegan)
load("../results/numerical/environmental-fit.R")
load("../results/numerical/bioclim-correlations.R")
```

@@

>>>>

```{r}
library(vegan); library(tidyverse)
load("../results/numerical/environmental-fit.R")
load("../results/numerical/bioclim-correlations.R")
```

@@

## Tables

```{r echo = FALSE, fig.cap = "**Figure 1** Study system."}
read.csv("../results/tables/T1 - Summary of the GLM models of species presence.csv", check.names = FALSE) %>%
  kableExtra::kbl(caption = "Table 1 Summary of the GLM models of species presence") %>%
  kableExtra::kable_classic(., full_width = F)
```
